{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}

### 2024-09-17 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, updated notes, work home sync
/w\, work home sync

            This produces the new updates for $x_{t +1}$, making it the same as the stated similar triangle form. 

@@

>>>>

            This produces the new updates for $x_{t +1}$, making it the same as the stated similar triangle form as in 
                {Definition \ref*{def:s-cvx_similar_triangle_form}}. 

@@

        Proposed by Chambolle, Dossal \cite{chambolle_convergence_2015}, we have the following representation of the Nesterov accelerated gradient: 
        \begin{definition}[FISTA]\label{def:fista}
            The FISTA algorithm has iterates such that they satisfy the following conditions recursively: 
                z_{n + 1} &= y_n - L^{-1}\mathcal G_L(y_n)
                x_{n + 1} &= z_n + t_{n +1} (z_{n + 1} - z_n), 
                y_{n + 1} &= \left(
                    1 - \frac{1}{t_{n + 1}}
                \right)z_{n + 1} + \left(
                    \frac{1}{t_{n + 1}}
                \right)x_{n + 1}
            where $(t_n)_{n\in \N}$ satisfies: $t_{n + 1}^2 - t_n^2 \le t_n$. 
            Observe the fact that the updates of the iterates resemble the similar triangle form in
        \begin{theorem}[FISTA as a special case of similar triangle form]
        \label{thm:fista_spacial_case_of_similar_triangle}
            if the stepsize $L\eta_n = t_n - 1$, and $\tilde \eta_{n + 1} = L^{-1} + \eta_n$, then
            \hyperref[def:fista]{Definition \ref*{def:fista}}
            is an example of 
